### 2024-03-08 docs/manuscript/manuscript.qmd
added refrences to discussion

However, the mediating analysis showed that total muscle mass diminished the main observed effect of body fat on physical fitness, with more muscled individuals displaying a better physical performance despite the body fat percentage. This finding suggests that older adults could be benefited of activities that promotes their muscle mass conservation, even when they have high body fat percentages [cita requerida]. Nevertheless, caution is advised in the interpretation of this result, as the close physiological association among increasing body fat and decreasing muscle mass during aging have been well-studied [cita requerida: sarcopenic obesity]

@@

Furthermore, the increase in body fat percentage was related to a reduced sympathetic activity and a higher parasympathetic activity during TMST, as hypothesized (i.e., SNS index, SI, SDNN and RMSSD). Throughout the course of physical efforts, ANS is expected to shift into a sympathetic predominance, ensuring a sufficient response to higher metabolic demands [@pmid:33246163]. However, aged individuals may present an impaired ANS response to physical exercise [@ijerph20054456]. In that sense, our results support that body composition plays a role in autonomic response. Moreover, they suggest that the negative effects of body fat on physical fitness in older adults, may be partially attributable to less efficient autonomic inputs to the cardiovascular system [cita requerida].

@@

As far as we know, there are not preceding studies addressing these findings. We posit that there exists further factors influencing the mediation effect. For instance, body distribution of the adipose tissue was not explored, specially when it is known that visceral fat has an important impact on cardiovascular health and its autonomic regulation [cita requerida]. Participants with higher fitness may have a different fat distribution compared with lower performance individuals, which may induce different effects on autonomic drive to the heart [cita requerida]. Furthermore, other physical physiological, demographic or psychological variables may be playing an unexplored role. However, these hypothesis must be examined under scientific standards. Therefore, exhaustive research is needed to address this intriguing interplay.

>>>>

However, the mediating analysis showed that total muscle mass diminished the main observed effect of body fat on physical fitness, with more muscled individuals displaying a better physical performance despite the body fat percentage. This finding suggests that older adults could be benefited of activities that promotes their muscle mass conservation, even when they have high body fat percentages [pmid:27663845].  Nevertheless, caution is advised in the interpretation of this result, as the close physiological association among increasing body fat and decreasing muscle mass during aging have been well-studied [@pmid:33335909]

@@

Furthermore, the increase in body fat percentage was related to a reduced sympathetic activity and a higher parasympathetic activity during TMST, as hypothesized (i.e., SNS index, SI, SDNN and RMSSD). Throughout the course of physical efforts, ANS is expected to shift into a sympathetic predominance, ensuring a sufficient response to higher metabolic demands [@pmid:33246163]. However, aged individuals may present an impaired ANS response to physical exercise [@ijerph20054456]. In that sense, our results support that body composition plays a role in autonomic response. Moreover, they suggest that the negative effects of body fat on physical fitness in older adults, may be partially attributable to less efficient autonomic inputs to the cardiovascular system [@pmid:36875496].

@@

As far as we know, there are not preceding studies addressing these findings. We posit that there exists further factors influencing the mediation effect. For instance, body distribution of the adipose tissue was not explored, specially when it is known that visceral fat has an important impact on cardiovascular health and its autonomic regulation [@pmid:31553779; pmid:32158768]. Participants with higher fitness may have a different fat distribution compared with lower performance individuals, which may induce different effects on autonomic drive to the heart [@pmid:19752873]. Furthermore, other physical physiological, demographic or psychological variables may be playing an unexplored role. However, these hypothesis must be examined under scientific standards. Therefore, exhaustive research is needed to address this intriguing interplay.
